Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems

### 2024-06-18 final/oup-authoring-template.tex
Add funding

\section{Author contributions statement}

Must include all authors, identified by initials, for example:
S.R. and D.A. conceived the experiment(s),  S.R. conducted the experiment(s), S.R. and D.A. analysed the results.  S.R. and D.A. wrote and reviewed the manuscript.

\section{Acknowledgments}
The authors thank the anonymous reviewers for their valuable suggestions. This work is supported in part by funds from the National Science Foundation (NSF: \# 1636933 and \# 1920920).

>>>>

\section{Acknowledgments}
The authors thank the anonymous reviewers for their valuable suggestions.
This work was supported in part by funds from
the Agencia I+D+i (PICT-2018-01516),
and Universidad de Buenos Aires (UBAINT Doctoral, REREC-2023-593-E-UBA-REC).
